\LARGE \bf Influence of child-robot spacial arrangement in a learning by teaching task

### 2016-02-02 paper-Ro_Man-2016.tex
add outline
advances on intro and measures

@@

We have 3 conditions following Kendon's F formation: 
\begin{itemize}
\item side by side
\item face to face
\item in L shape
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
Cowriter

@@

\section{RELATED WORKS}
Proxemics

@@

We propose to study the impact of spatial arrangement on engagement of children a handwriting task
\section{APPROACH}

within subject, 2 robots in front of the child who has to teach to the two robots

@@

\section{METHOD}

@@

\subsection{Seriousness}

\subsection{With-me-ness}
Present it as a measure of synchrony,

@@

\subsection{Questionnaire on likeability and Interrelationship}

@@

>>>>

\usepackage[pdftex]{graphicx}
%\graphicspath{}

@@

We have 3 conditions following Kendon's F formation: 
\begin{itemize}
\item side by side
\item face to face
%\item in L shape
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
Interaction settings are crucial for

The Co-Writer projects aims to help children with difficulties in handwriting \cite{hood2015when}. 
It is based on the idea of learning by teaching. 
By teaching a Nao robot how to write, children learn and improve their handwriting. 
The activity also plays with the protégé effect that make children more motivated in practising for the robot than for themselves.

Previous studies in the Co-Writer project helped us to develop a system that generates handwriting for the robot based on demonstrations from the child\cite{hood2015when}. 
Case studies presented in \cite{jacq2016building} showed that children were able to stay engaged in long term interaction with repeated session within the Co-Writer activity in real pedagogical/therapeutic contexts. 
These works proved to have a positive effect on extrinsic motivation of children when practising their handwriting thanks to the protégé effect.

@@

Proxemics

@@

We propose to study the impact of spatial arrangement on engagement of children a handwriting task

\section{RELATED WORKS}

Perspective taking: speaker with partners tend yo use more egocentric perspective rather than solo speakers \cite{Schober}

Handwriting linked to spatial-sequential ability of the child. 
This is also linked to perspective taking ability of the child.

The 3 spatial perspective taking rules state that :
\begin{enumerate}
\item any object will present the same visual appearance to the self and to another person if the two observer view from the same point of view.
\item An object with different sides will be seen different if the viewers are form different side views
\item An object homogeneous in all sides will be the same from different view. 
\end{enumerate}

\cite{Newcombe1992} shows that children around the age of 5 are able to complete perspective taking tasks and to imagine what others point of you might look like.

\section{APPROACH}
In this study, each child saw interacted with the robot in the two conditions in a random order.

within subjects Repeated measures

@@

\section{METHOD}
25

Number of child
Expe settings
Condition within subject but with 
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{./figures/s2s_photo.jpg}
\caption[Side by SIde Condition]{}
\caption{}
\label{fig:s2s_photo}
\end{figure}

@@

\subsection{Reward Mechanism}
The table interface on which the child and the robot practice their handwriting contains also two buttons that allow the child to give positive (green thumb-up) or negative (red thumb-down) feeback to the robot's handwriting.

We noticed that children were expetcing the robot to react. 
Now that the usage of these buttons have been proven, we will consider for futur experimemnt to allow the robot to react. 
For instance, if the child gives a positive feedback when the robot is actually improving, the robot should display a positive emotion.
If he is given a positive feedback but doesnt not actually make any progree, he might express doubt to force the child to be more exigeant.

\subsection{With-me-ness}
\cite{lemaignan2016realtime}
Present it as a measure of synchrony,

@@

%\subsection{Questionnaire on likeability and Interrelationship}

@@

ref all cowriter paper + paper of sharma sur withmeness
